---
title: "Fine-scale heterogeneity in Schistosoma mansoni force of infection measured through antibody response"
subtitle: "Figure 1, Figure S2, Figure S3 maps with model based geostatistics"
author: "Ben Arnold ben.arnold@ucsf.edu"
date: "run `r Sys.time()`"
output: 
  html_document:
    highlight: haddock
    theme: default
    code_folding: hide
    df_print: paged
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


# Preamble
```{r preamble}
library(here)
here()
#--------------------------------
# source the configuration file
#--------------------------------
source(here("R/mbita-schisto-Config.R"))
```


# Load and process data
```{r load data,message=FALSE,warning=FALSE}
#---------------------------
# Mbita public schisto data
#---------------------------
d <- readRDS(here("data","mbita_schisto.rds") )

#---------------------------
# Mbita village coordinates
# (not provided publicly)
#---------------------------
d_lonlat <- readRDS(here("data","mbita_lonlat.rds") )


#---------------------------
# merge village coordinates
# onto the schistosomiasis 
# data
d <- left_join(d,d_lonlat,by="vid")


#---------------------------
# register survey data
# as an sf object
#---------------------------
dsf <- d %>% 
  group_by(vid) %>%
  dplyr::select(vid,lon,lat) %>%
  slice(1) %>%
  st_as_sf(coords = c("lon","lat")) %>%
  st_set_crs(4326)

#---------------------------
# Identify the convex hull
# around villages and make
# a polygon
#---------------------------
xycoords <- as.matrix(d[,c('lon','lat')])
xychull <- xycoords[chull(xycoords),]
xypoly <- st_polygon(list(rbind(xychull,xychull[1,]))) %>%
  st_sfc() %>% st_sf() %>% st_set_crs(4326)

#---------------------------
# identify a rectangle around
# the villages 
# this is used as a bounding
# box for all mapping and
# predictions below
#---------------------------
lon1 <- 33.94
lon2 <- 34.52
lat1 <- -0.55
lat2 <- -0.3207

xysquare <- rbind( c(lon1,lat1),
                   c(lon1,lat2),
                   c(lon2,lat2),
                   c(lon2,lat1)
                   )

xysqpoly <- st_polygon(list(rbind(xysquare,xysquare[1,]))) %>%
  st_sfc() %>% st_sf() %>% st_set_crs(4326)

#---------------------------
# Calculate the approximate
# area of the study region
#---------------------------
studyarea <- st_area(xypoly)
studyarea # study area in m2
studyarea/(1000^2) # study area in km2

#---------------------------
# Retrieve elevation data
#
# if data are not already
# downloaded, the raster 
# package will download them
# into the /data directory
#---------------------------
library(raster)
dxy <- st_coordinates(dsf)
elev <- raster::getData("alt", country="Kenya",path=here("data"))
elev2 <- crop(elev,xysqpoly)

#---------------------------
# Retrieve WorldClim data
# average monthly minimum temp
# average monhtly precip
#
# if data are not already
# downloaded, the raster 
# package will download them
# into the /data directory
#---------------------------
tmin <- raster::getData('worldclim', var='tmin', res=0.5, lon=mean(dxy[,1]), lat=mean(dxy[,2]), path=here("data"))
tmin2 <- mean(crop(tmin, elev2))

prec <- raster::getData('worldclim', var='prec', res=0.5, lon=mean(dxy[,1]), lat=mean(dxy[,2]), path=here("data"))
prec2 <- mean(crop(prec, elev2))

#---------------------------
# retreive extent of
# lake Victoria
# computed from the global
# surface water dataset
# with a raster->polygon
# transformation in Google EE
#---------------------------
lvictoria <- sf::st_read(here("data","mbita_gswpoly.geojson"),crs=4326) 

# there are 31 polygons in the feature collection
# but there is really just one single large polygon that contains the main lake
# filter to polygons with more than 500 pixels to identify this feature
lvictoria <- lvictoria %>%
  filter(count>500)

#---------------------------
# Create an interpolation
# grid of points over the
# study region rectangle
# use the feature rasters
# as the base
#
# This grid is used to
# make model predictions
# later in the analysis (below)
#---------------------------
interp_grid <- raster::aggregate(elev2, 1)
interp_grid <- data.frame(lon = coordinates(interp_grid)[,1], 
                          lat = coordinates(interp_grid)[,2],
                          elev=interp_grid[],
                          tmin=aggregate(tmin2, 1)[],
                          prec=aggregate(prec2, 1)[]
                          )

# sf object of the interpolation grid
gridsf <- st_as_sf(interp_grid,coords = c("lon","lat")) %>%
  st_set_crs(4326) %>%
  st_intersection(xysqpoly) 

# calc the minimum dist from each point to lake victoria
dist_victoria <- apply(st_distance(gridsf,lvictoria),1,min)
gridsf <- gridsf %>% 
  mutate(dist_victoria = dist_victoria)

# save the interpolation grid as a data.frame for modeling
gridxy <- st_coordinates(gridsf)
pred_grid <- data.frame(gridsf,lon=gridxy[,1],lat=gridxy[,2]) %>% 
  dplyr::select(-geometry)


#---------------------------
# join geospatial layers
# to the village data
#---------------------------
dsf$elev <- raster::extract(elev2,dxy)
dsf$tmin <- raster::extract(tmin2,dxy)
dsf$prec <- raster::extract(prec2,dxy)

# estimate distance to lake victoria
vil_dist_victoria <- st_distance(dsf,lvictoria)
dsf$dist_victoria <- vil_dist_victoria

#---------------------------
# collapse to counts at the
# village level, by year
# calculate prevalence
# by SEA and Kato-Katz
#
# also summarize by village
# over all years
#---------------------------
dvil <- d %>%
  group_by(vid,year) %>%
  summarize(sea_n = sum(sea_pos,na.rm=T),
            sea_N = sum(ifelse(!is.na(sea_pos),1,0)),
            kk_n = sum(kk_pos,na.rm=T),
            kk_N = sum(ifelse(!is.na(kk_pos),1,0)),
            lon = mean(lon),
            lat = mean(lat)
            ) %>%
  mutate(sea_prev = sea_n/sea_N,
         kk_prev = kk_n/kk_N,
         yearf = as.factor(year))

dvil2 <- d %>%
  group_by(vid) %>%
  summarize(sea_n = sum(sea_pos,na.rm=T),
            sea_N = sum(ifelse(!is.na(sea_pos),1,0)),
            kk_n = sum(kk_pos,na.rm=T),
            kk_N = sum(ifelse(!is.na(kk_pos),1,0)),
            lon = mean(lon),
            lat = mean(lat)
            ) %>%
  mutate(sea_prev = sea_n/sea_N,
         kk_prev = kk_n/kk_N)

#---------------------------
# merge on the geospatial 
# layers
#---------------------------
dvil <- left_join(dvil,dsf,by="vid")
dvil2 <- left_join(dvil2,dsf,by="vid")

#---------------------------
# save a village-level
# dataset that includes
# geospatial layers
#---------------------------
dvil_spatial <- dvil2 %>%
  dplyr::select(vid,elev,tmin,prec,dist_victoria)
saveRDS(dvil_spatial,file=here("data","mbita_spatial.rds"))
write_csv(dvil_spatial,path=here("data","mbita_spatial.csv"))
```

# Figure S2

## Assess bivariate relationships between covariates and outcomes

```{r covariate pairs plot, fig.width=8,fig.height=8}
#----------------------------------
# correlation ellipse
#----------------------------------
myellipse<-function(x,y,...){
  maxx <- max(x,na.rm=TRUE)
  minx <- min(x,na.rm=TRUE)
  maxy <- max(y,na.rm=TRUE)
  miny <- min(y,na.rm=TRUE)
  midx <- (maxx+minx)/2
  midy <- (maxy+miny)/2
  corxy <- cor(x,y,method="spearman",use="pairwise.complete.obs")
  colgroup<-cut(corxy,breaks=seq(-1,1,length=11),labels=F)
  brewcols <- brewer.pal(n=11,"RdYlGn")
  cols<-brewcols[colgroup]
  xyc <-sprintf("%1.2f",corxy)
  xyc[grep("NA",xyc)]<-""
  exy <- ellipse(corxy,centre=c(midx,midy),scale=c((maxx-minx)/6,(maxy-miny)/6))
  polygon(exy,col=alpha(cols,alpha=0.5))
  lines(exy)
  if(!is.na(corxy)) {
    if(corxy<0.8) {
      text(midx,midy,xyc,cex=1.3)
    } else{
      text(maxx,midy-((maxy-miny)/3),xyc,cex=1.3,adj=1)
    }
  }
  
}


#----------------------------------
# scatter plot with loess fit
# (trimmed to reduce edge effects)
#----------------------------------
scatterloess<-function(x,y,cex=0.4,...){
  ld <- data.frame(x,y)
  ld <- ld[complete.cases(ld),]
  if(nrow(ld)>0) {
    points(ld$x,ld$y,pch=19,cex=cex,col=alpha('black',alpha=1))
    lfit <- loess(y~x,data=ld)
    xqs <- quantile(x,probs=c(0.01,0.99),na.rm=TRUE)
    px <- seq(xqs[1],xqs[2],by=0.01)
    py <- predict(lfit,newdata=data.frame(x=px))
    lines(px,py,col="gray20",lwd=1.5)
  }
  
}

#----------------------------------
# Subset variables for pairs plot
#----------------------------------
hmat <- dvil2 %>%
  ungroup() %>%
  dplyr::select(sea_prev,kk_prev,dist_victoria,elev,tmin,prec)

#----------------------------------
# print correlation matrix
#----------------------------------
round(cor(hmat,method="spearman"),3)


#----------------------------------
# Make a pairs plot
#----------------------------------
pairs_labs <- c("SEA\nseroprevalence","Kato-Katz\nprevalence","Distance to\nLake Victoria","Elevation","Temperature","Precipitation")
pairs(hmat,cex=0.4,las=1, 
      labels = pairs_labs,
      upper.panel=scatterloess,
      lower.panel=myellipse
)

```

```{r output pairs plot, eval=TRUE,echo=FALSE,warnings=FALSE}
pdf(here("output","mbita-covariate-pairs.pdf"),width=10,height=10)
pairs(hmat,cex=0.4,las=1, 
      labels = pairs_labs,
      upper.panel=scatterloess,
      lower.panel=myellipse
)
dev.off()
```

# Model based geostatistics

The predictions below are prevalence. In addition to a village's location, the model uses information about elevation (SRTM 90), precipitation (WorldClim average), temperature (WorldClim min), and distance to Lake Victoria (global surface water layer). The model uses a low rank Gaussian process to interpolate between locations.


## SEA seroprevalence

### SEA geospatial model fit
```{r model sea seroprevalence}
# gaussian process / spline model fit
# village-level data
dvil3 <- dvil %>%
  mutate(dummy = 1,
         vidf = factor(vid,levels=unique(dvil$vid))
         )

#  + s(elev,k=3)
fit_sea <- gam(cbind(sea_n,sea_N-sea_n) ~ s(lat,lon, k=-1,bs="gp") + s(dist_victoria,k=3) + s(tmin,k=3) + s(prec,k=3) , 
                   family="binomial",
                   data=dvil3,
                   method="REML",
                   select=TRUE)

# summarize model output
summary(fit_sea)

```

### SEA geospatial model predictions
```{r predict sea seroprevalence}
# model predictions at village points
dvil3$pred_sea <- predict(fit_sea,type="response")

# model predictions over the entire prediction grid
pred_sea <- predict(fit_sea,newdata=pred_grid,type="response",se=TRUE)

rast_sea <- SpatialPixelsDataFrame(points=pred_grid[c("lon","lat")],data=data.frame(fit=pred_sea$fit*100,se=pred_sea$se.fit),proj4string=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))

```


## Kato-Katz prevalence

### KK geospatial model fit
```{r model kato-katz prevalence}
# gaussian process / spline model fit
#  s(elev,k=3) +
fit_kk <- gam(cbind(kk_n,kk_N-kk_n) ~ s(lat,lon, k=-1,bs="gp") + s(dist_victoria,k=3) + s(tmin,k=3) + s(prec,k=3),  
                   family="binomial",
                   data=dvil3,
                   method="REML",
                   select=TRUE)

summary(fit_kk)


```

### KK geospatial model predictions
```{r predict kato-katz prevalence}
# model predictions at village points
dvil3$pred_kk <- predict(fit_kk,type="response")

# model predictions at interpolation grid
pred_kk <- predict(fit_kk,newdata=pred_grid,type="response",se=TRUE)
rast_kk <- SpatialPixelsDataFrame(points=pred_grid[c("lon","lat")],data=data.frame(fit=pred_kk$fit*100,se=pred_kk$se.fit),proj4string=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))

```

# Figure 1

## Overview map
Overview of the study region

```{r overview map, out.width = "100%"}
xlon <- mean(lon1,lon2)
ylat <- mean(lat1,lat2)
map_overview <- leaflet(width = "100%") %>%
  addProviderTiles("Esri.WorldTopoMap",options=providerTileOptions(opacity=1)) %>%
  setView(lng = xlon, lat = ylat, zoom = 6) %>%
  addRectangles(
    lng1=lon1, lat1=lat2,
    lng2=lon2, lat2=lat1,
    fillColor = "transparent",weight=2,color="red"
  ) %>%
  addScaleBar(position="bottomright",options=scaleBarOptions(imperial = FALSE))

# Stamen.TonerLite 
map_overview

```

## Points map (SEA + KK)

Map village locations, colored by SEA seroprevalence and Kato-Katz prevalence
```{r points map with leaflet, out.width = "100%"}

xlon <- mean(dvil2$lon)
ylat <- mean(dvil2$lat)
pointpal <- colorNumeric(
  palette = "viridis",
  domain=c(0,max(dvil2$sea_prev*100)),
  na.color = "transparent",
)
pointpal_rev <- colorNumeric(
  palette = "viridis",
  domain=c(0,max(dvil2$sea_prev*100)),
  na.color = "transparent",
  reverse = TRUE
)
map_points <- leaflet(width = "100%") %>%
  addProviderTiles("CartoDB.Positron",options=providerTileOptions(opacity=1)) %>%
  setView(lng = xlon, lat = ylat, zoom = 11) %>%
  addCircleMarkers(data = dvil2, group = "SEA seroprevalence",
                   lng = ~ lon, lat = ~ lat,
                   color = ~pointpal(sea_prev*100), 
                   weight=1,fillOpacity = 0.8,
                   radius=4
              ) %>%
  addCircleMarkers(data = dvil2, group = "Kato Katz prevalence",
                   lng = ~ lon, lat = ~ lat,
                   color = ~pointpal(kk_prev*100), 
                   weight=1,fillOpacity = 0.8,
                   radius=4
              ) %>%
  addRectangles(
    lng1=lon2, lat1=lat1,
    lng2=lon1, lat2=lat2,
    fillColor = "transparent",weight=2,color="black"
  ) %>%
  addScaleBar(position="bottomleft",options=scaleBarOptions(imperial = FALSE)) %>%
  addLegend(position="bottomright",
            pal = pointpal_rev, 
            values= c(0,max(dvil2$sea_prev*100)),
            labFormat = labelFormat(transform = function(x) sort(x, decreasing = TRUE)),
            title = "SEA (%)",
            group = "SEA seroprevalence"
            ) %>%
  addLegend(position="bottomright",
            pal = pointpal_rev, 
            values= c(0,max(dvil2$sea_prev*100)),
            labFormat = labelFormat(transform = function(x) sort(x, decreasing = TRUE)),
            title = "Kato-Katz (%)",
            group="Kato Katz prevalence"
            ) %>%
  # add layer controls
  addLayersControl(overlayGroups = c("SEA seroprevalence", "Kato Katz prevalence"), 
                   position="topleft",
                   options = layersControlOptions(collapsed=FALSE)) %>% 
  hideGroup("Kato Katz prevalence")

map_points

```

##  Predicted surface, SEA
```{r map surface SEA, out.width = "100%"}

# separate raster layers for prevalence and SE
rast_seap <- raster::raster(rast_sea,layer=1)
rast_sease <- raster::raster(rast_sea,layer=2)

dvil3_2014 <- dvil3 %>%
  filter(year==2014)


#---------------------------
# Buffer around Lake Victoria, 1500m
# doesn't really work
# but leaving the code in
# for now
#---------------------------
# lvictoria_1500m  <- lvictoria %>%
#   st_boundary() %>%
#   st_transform(crs="+proj=utm +zone=37 +datum=NAD83 +units=m +no_defs") %>%
#   st_buffer(dist=1500,mitreLimit=0.1) %>%
#   st_transform(crs=4326)

# define the color palettes for prevalence and SE
# reverse palettes are there just for the legend
# so that we can present high values on the top
markerscale <- 1
pal <- colorNumeric(
  palette = "viridis",
  domain=c(0,values(rast_seap)),
  na.color = "transparent"
)
pal_rev <- colorNumeric(
  palette = "viridis",
  domain=c(0,values(rast_seap)),
  na.color = "transparent",
  reverse = TRUE
)
palse <- colorNumeric(
  palette = "magma",
  domain=values(rast_sease),
  na.color = "transparent",
  reverse=TRUE
)
palse_rev <- colorNumeric(
  palette = "magma",
  domain=values(rast_sease),
  na.color = "transparent",
  reverse = FALSE
)

# make the map
map_sea <- leaflet(width = "100%") %>% 
  # addProviderTiles("CartoDB.Positron",options=providerTileOptions(opacity=1)) %>%
  # addTiles("https://cartodb-basemaps-{s}.global.ssl.fastly.net/light_all/{z}/{x}/{y}{r}.png") %>%
  setView(lng = xlon, lat = ylat, zoom = 11) %>%
  addRasterImage(rast_seap,colors=pal,opacity=0.6,group="Prevalence") %>%
  addRasterImage(rast_sease,colors=palse,opacity=0.6,group="Standard Error") %>%
  addPolygons(data = lvictoria,
              fill = TRUE,fillColor = "#D4DADC", fillOpacity=1, opacity=0
              ) %>%  #   #99B3CC
  addRectangles(
    lng1=lon2, lat1=lat1,
    lng2=lon1, lat2=lat2,
    fillColor = "transparent",weight=2,color="black"
  ) %>%
  addCircleMarkers(data = dvil3_2014,
                   lng = ~ lon, lat = ~ lat,
                   # radius = markerscale*sqrt((dvil3_2014$sea_prev*100)/pi),
                   radius = 4,
                   color = ~'black', fill = ~ NA, weight=1,opacity = 1
                   # remove pop ups to protect confidentiality.
                   # popup=paste(dvil3_2014$vid, "<br>",
                   #             "N pos / tested: ", dvil3_2014$sea_n," / ",dvil3_2014$sea_N,"<br>",
                   #       "SEA seroprevalence: ", sprintf("%1.0f",dvil3_2014$sea_prev*100),"%","<br>",
                   #       "predicted: ",sprintf("%1.0f",dvil3_2014$pred_sea*100),"%",sep="")
              ) %>%
  
  # add scale bar and legends
  addScaleBar(position="bottomleft",options=scaleBarOptions(imperial = FALSE)) %>%
  addLegend(position="bottomright",
            pal = pal_rev, 
            values= c(0,values(rast_seap)),
            labFormat = labelFormat(transform = function(x) sort(x, decreasing = TRUE)),
            title = "SEA (%)",
            group = "Prevalence"
            ) %>%
  addLegend(position="bottomright",
            pal = palse_rev, 
            values= values(rast_sease),
            labFormat = labelFormat(transform = function(x) sort(x, decreasing = TRUE)),
            title = "SE",
            group="Standard Error"
            ) %>%
  # add layer controls
  addLayersControl(overlayGroups = c("Prevalence", "Standard Error"), 
                   position="topleft",
                   options = layersControlOptions(collapsed=FALSE)) %>% 
  hideGroup("Standard Error")


map_sea


```


## Observed vs Predicted SEA
```{r sea obsvpred figure}
# Make a figure of village level predicted prevalence versus observed prevalence 
# estimate spearman rank correlation
seacor <- cor(dvil3_2014$sea_prev,dvil3_2014$pred_sea,method="spearman") 

# plot predicted versus observed
ovp_sea <- ggplot(data=dvil3_2014,aes(x=sea_prev,y=pred_sea)) +
  geom_abline(slope=1,intercept=0,lty="dashed",alpha=0.5)+
  geom_point(color="black",alpha=0.7,size=4)+
  scale_y_continuous(breaks=seq(0,1,by=0.2),labels=seq(0,100,by=20))+
  scale_x_continuous(breaks=seq(0,1,by=0.2),labels=seq(0,100,by=20))+
  annotate(geom="text",x=0.2,y=0.8,size=10,label=paste("rho ==",sprintf("%1.2f",seacor)),parse=TRUE)+
  coord_cartesian(ylim=c(0,1),xlim=c(0,1))+
  labs(y="predicted SEA seroprevalence (%)",x="observed SEA seroprevalence (%)") +
  theme_gray(base_size = 20) 
ovp_sea


# save a png file
ggsave(here("output","mbita-spatialGAM-pred-v-obs-SEA.png"),ovp_sea,device="png",width=6,height=6)


```

# Figure S1

##  Predicted surface, Kato-Katz
```{r map surface KK, out.width = "100%"}

# separate raster layers for prevalence and SE
rast_kkp <- raster::raster(rast_kk,layer=1)
rast_kkse <- raster::raster(rast_kk,layer=2)


# define the color palettes for prevalence and SE
# reverse palettes are there just for the legend
# so that we can present high values on the top
markerscale <- 1
kkpal <- colorNumeric(
  palette = "viridis",
  domain=c(0,values(rast_kkp)),
  na.color = "transparent"
)
kkpal_rev <- colorNumeric(
  palette = "viridis",
  domain=c(0,values(rast_kkp)),
  na.color = "transparent",
  reverse = TRUE
)
kkpalse <- colorNumeric(
  palette = "magma",
  domain=values(rast_kkse),
  na.color = "transparent",
  reverse=TRUE
)
kkpalse_rev <- colorNumeric(
  palette = "magma",
  domain=values(rast_kkse),
  na.color = "transparent",
  reverse=FALSE
)

# make the map
map_kk <- leaflet(width = "100%") %>% 
  # addProviderTiles("CartoDB.Positron",options=providerTileOptions(opacity=1)) %>%
  # addTiles("https://cartodb-basemaps-{s}.global.ssl.fastly.net/light_all/{z}/{x}/{y}{r}.png") %>%
  setView(lng = xlon, lat = ylat, zoom = 11) %>%
  addRasterImage(rast_kkp,colors=kkpal,opacity=0.6,group="Prevalence") %>%
  addRasterImage(rast_kkse,colors=kkpalse,opacity=0.6,group="Standard Error") %>%
  addPolygons(data = lvictoria,
              fill = TRUE,fillColor ="#D4DADC", fillOpacity=1, opacity=0
              ) %>%  #  "#99B3CC"
  addRectangles(
    lng1=lon2, lat1=lat1,
    lng2=lon1, lat2=lat2,
    fillColor = "transparent",weight=2,color="black"
  ) %>%

  addCircleMarkers(data = dvil3_2014,
                   lng = ~ lon, lat = ~ lat,
                   # radius = markerscale*sqrt((dvil3_2014$kk_prev*100)/pi),
                   radius = 4,
                   color = ~'black', fill = ~ NA, weight=1, opacity = 1
                   # remove pop ups to protect confidentiality.
                   # popup=paste(dvil3_2014$vid, "<br>",
                   #             "N pos / tested: ", dvil3_2014$kk_n," / ",dvil3_2014$kk_N,"<br>",
                   #       "Kato-Katz prevalence: ", sprintf("%1.0f",dvil3_2014$kk_prev*100),"%","<br>",
                   #       "predicted: ",sprintf("%1.0f",dvil3_2014$pred_kk*100),"%",sep="")
              ) %>%
  
  # add scale bar and legends
  addScaleBar(position="bottomleft",options=scaleBarOptions(imperial = FALSE)) %>%
  addLegend(position="bottomright",
            pal = kkpal_rev, 
            values= c(0,values(rast_kkp)),
            labFormat = labelFormat(transform = function(x) sort(x, decreasing = TRUE)),
            title = "Kato-Katz (%)",
            group = "Prevalence"
            ) %>%
  addLegend(position="bottomright",
            pal = kkpalse_rev, 
            values= values(rast_kkse),
            labFormat = labelFormat(transform = function(x) sort(x, decreasing = TRUE)),
            title = "SE",
            group="Standard Error"
            ) %>%
  # add layer controls
  addLayersControl(overlayGroups = c("Prevalence", "Standard Error"), 
                   position="topleft",
                   options = layersControlOptions(collapsed=FALSE)) %>% 
  hideGroup("Standard Error")


map_kk


```

## Observed vs Predicted Kato-Katz
```{r kk obsvpred figure}
# Make a figure of village level predicted prevalence versus observed prevalence 
# estimate spearman rank correlation
kkcor <- cor(dvil3_2014$kk_prev,dvil3_2014$pred_kk,method="spearman") 

# plot predicted versus observed
ovp_kk <- ggplot(data=dvil3_2014,aes(x=kk_prev,y=pred_kk)) +
  geom_abline(slope=1,intercept=0,lty="dashed",alpha=0.5)+
  geom_point(color="black",alpha=0.7,size=4)+
  scale_y_continuous(breaks=seq(0,1,by=0.2),labels=seq(0,100,by=20))+
  scale_x_continuous(breaks=seq(0,1,by=0.2),labels=seq(0,100,by=20))+
  annotate(geom="text",x=0.2,y=0.8,size=10,label=paste("rho ==",sprintf("%1.2f",kkcor)),parse=TRUE)+
  coord_cartesian(ylim=c(0,1),xlim=c(0,1))+
  labs(y="predicted Kato-Katz prevalence (%)",x="observed Kato-Katz prevalence (%)") +
  theme_gray(base_size = 20) 
ovp_kk


# save a png file
ggsave(here("output","mbita-spatialGAM-pred-v-obs-KK.png"),ovp_kk,device="png",width=6,height=6)


```


# Session Info
```{r session info}
sessionInfo()
```
