---
title: "Fine-scale heterogeneity in Schistosoma mansoni force of infection measured through antibody response"
subtitle: "Fig 4c, Fig 4d, Fig S5 seroprevalence and force of infection by age"
author: "Ben Arnold ben.arnold@ucsf.edu"
date: "run `r Sys.time()`"
output:
  html_document:
    highlight: haddock
    theme: default
    code_folding: hide
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


# Preamble
```{r preamble}
library(here)
here()
#--------------------------------
# source the configuration file
# and the shared functions file
#--------------------------------
source(here("R/mbita-schisto-Config.R"))
source(here("R/mbita-schisto-Functions.R"))
```



# Load Mbita Kenya antibody measurements

These data include measurements from pre-school aged children in 30 villages near Homa Bay and Mbita in Western Kenya. This article summarizes the study design and field methods:

Won KY, Kanyi HM, Mwende FM, Wiegand RE, Brook Goodhew E, Priest JW, et al. Multiplex Serologic Assessment of Schistosomiasis in Western Kenya: Antibody Responses in Preschool Age Children as a Measure of Reduced Transmission. _Am J Trop Med Hyg._ 2017; 16–0665. https://www.ncbi.nlm.nih.gov/pubmed/28719280

```{r load data, warning=FALSE}
#-----------------------------------
# load the child antibody and 
# kato-katz measurements
#-----------------------------------
d <- readRDS(here("data","mbita_schisto.rds"))

#-----------------------------------
# load the village-level spatial
# covariate data, created with
# mbita-schisto-map.Rmd
#
# note: for public-facing workflow
# this file does not include village 
# lon/lat to protect participant
# confidentiality
#-----------------------------------
d_spatial <- readRDS(here("data","mbita_spatial.rds"))

d2 <- d %>%
  left_join(d_spatial,by="vid")

# create age strata
# create log values for SEA MFI and KK epg
# convert the dist_victoria variable from class units to numeric
d2 <- d2 %>%
  mutate(agecat = cut(agey,breaks=c(0,1,2,3,4,6),
                      labels=c("<1 year","1 year","2 years","3 years","4 years")),
         logsea = log10(sea),
         logepg = log10(sm_epg),
         dist_victoria = as.numeric(dist_victoria)
         )

#----------------------------------
# prep data for model
#----------------------------------
d3 <- d2 %>% 
  ungroup() %>%
  mutate(vid=factor(vid),
         yearf = factor(year),
         dummy=1)


```


# Age stratified distributions

```{r density plot by age}

table(d2$agecat)

pdist <- ggplot(data=d2,aes(x=logsea)) +
  facet_grid(agecat~.) +
  geom_density(alpha=0.8,color=NA,fill=vircols[3]) +
  geom_rug(alpha=0.3,color = vircols[3]) +
  geom_vline(aes(xintercept = log10(965) ),lty=1) +
  # scale_fill_manual(values=pcols)+
  # geom_vline(aes(xintercept = mixcut),lty=2) +
  labs(x="log10 luminex response (MFI-bg)") +
  theme_minimal() + 
  theme(legend.position = "none",
        strip.text.y=element_text(angle=0))

pdist

```


# Age dependent seroprevalence

Estimate age-dependent seroprevalence using a semi-parametric spline fit.  Include community-level random effects to account for repeated measures within community. Estimate an approximate, simultaneous 95% confidence interval on the spline fit.

```{r agecurves model selection}

# constant rate (exponential) proportional hazards current status model
fit_exp <- mgcv::gam(sea_pos~1+ s(vid,bs="re",by=dummy),offset = log(agey), family=binomial(link = "cloglog"), data=d3)

# semiparamtric proportional hazards current status model
fit_age <- mgcv::gam(sea_pos~s(agey,bs="cr",k=9) + s(vid,bs="re",by=dummy), family=binomial(link = "cloglog"), data=d3)

# semiparamtric proportional hazards current status model plus fixed effects for study year
fit_age_yr <- mgcv::gam(sea_pos~ yearf + s(agey,bs="cr",k=9) + s(vid,bs="re",by=dummy), family=binomial(link = "cloglog"), data=d3)

# compare AIC and BIC to examine increased model complexity
AIC(fit_exp, fit_age, fit_age_yr)
BIC(fit_exp, fit_age, fit_age_yr)
```


```{r agecurves seroprev}
# Fit a proportional hazards current status survival model
# with semiparametric hazard by age, fixed effects for year,
# and random effects for village
fitp_sea <- mgcv::gam(sea_pos~ yearf + s(agey,bs="cr",k=9) + s(vid,bs="re",by=dummy), family=binomial(link = "cloglog"), 
                      data=d3)
newd <- d3 %>%  mutate(dummy=0, yearf = "2012")
fitp_seaci <- gamCI(m=fitp_sea,newdata=newd,nreps=10000)

# convert linear predictor to prevalance
fitp_seaci <- fitp_seaci %>%
  mutate(fit = cloglogfn(fit),
         uprP = cloglogfn(uprP),
         lwrP = cloglogfn(lwrP),
         uprS = cloglogfn(uprS),
         lwrS = cloglogfn(lwrS),
         )

```

Make a figure
```{r seroprev by age plot}

pageprev <- ggplot(data=fitp_seaci,aes(x=agey,y=fit)) +
  geom_ribbon(aes(ymin=lwrS,ymax=uprS),alpha=0.3,fill="gray40") +
  geom_line(lwd=0.5,alpha=1,color="gray40") +
  scale_y_continuous(breaks=seq(0,0.8,by=0.1),labels=seq(0,80,by=10))+
  labs(x="age, years",y="SEA seroprevalence (%)") +
  coord_cartesian(xlim=c(0,5),ylim=c(0,0.8))+
  theme_minimal() +
  theme(legend.position="none")

pageprev


```



# Age-specific force of infection (FOI)

Estimate the age-dependent seroconversion rate as a measure of force of infection (FOI) using a semi-parametric spline model. Estimate FOI using finite differences of the age-dependent seroprevalence curve for the derivative.


```{r estimate foi from seroprevalence}
#----------------------------
# estimate FOI for SEA
# from the spline model
#----------------------------

#----------------------------------------
# Model predictions of FOI, with age grid newd
#----------------------------------------
set.seed(123)
newd <- data.frame(agey=seq(0.2,5,by=0.01),vid="1",dummy=0, yearf = "2012")
foi_ests <- foiCI(m=fitp_sea,newdata=newd,fdvar="agey")

```

```{r foi by age figure}
foiplot <- ggplot(data=foi_ests,aes(x=agey,y=foi,ymin=foi_lwrBS,ymax=foi_uprBS)) +
  geom_ribbon(color=NA,alpha=0.3,fill="gray40") +
  geom_line(color="gray40") +
  scale_y_continuous(breaks=seq(0,0.6,by=0.1))+
  labs(x="age, years",y=expression(paste("age-specific seroconversion rate per year, ",lambda,"(a)")))+
  coord_cartesian(ylim=c(0,0.6))+
  theme_minimal()
foiplot
```

## Community-specific estimates

Estimate mean community-level force of infection, marginally adjusted over year and age.  Estimate the average force of infection from the seroprevalence curve using the basic relationship between the hazard (force of infection) and the cumulative hazard. 

The hazard or force of infection at age $a$ is: $\lambda(a) = F'(a)/(1-F(a))$. From the definition of the hazard, we have: 

$1- F(a) = \exp [ - \int_0^a \lambda(a) da ]$ and $\int_0^a \lambda(a) da = - \log [1-F(a)]$.

This is the cumulative hazard. The average hazard per year (units of $a$) also divided $-\log[1-F(a)]$ by $a$.  So, all of the information is embedded in the cumulative distribution function, $F(a)$, which here is the age-dependent seroprevalence curve. 

The average hazard over the age period $a_1=1$ to $a_2=5$ years is:

\begin{equation}
  \int_{a_1}^{a_2} \lambda(a) da = \frac{\log[1-F(a_1)]-\log[1-F(a_2)]}{a_2 - a_1}
\end{equation}

We estimate the variance of this parameter from a parametric bootstrap simulation of the posterior distributions of the spline parameters.  The function that implements this is `avgFOI` in the `mbita-schisto-Functions.R` script.

```{r community level foi estimates}
#------------------------------------
# obtain predictions from the seroprevalence model, 
# fit above in the earlier code chunk (fitp_sea)
#
# use predictions at ages 1 and 5 years to estimate the average FOI over the
# age range, where foi = [log(1-F(a1))-log(1-F(a2))] / (a2-a1) for a1=1, a2=5
# use a parametric bootstrap from the posterior of the vcov matrix to estimate
# uncertainty in the marginally averaged FOI. see the avgFOI() function in the 
# mbita-schisto-Functions.R script for details
#
# each community's prediction is shifted by its
# estimated random effect in the model (hence dummy=1, to include RE in prediction)
#------------------------------------
foi_community_ests <- foreach(vidi = levels(d3$vid), .combine = rbind) %do% {
  newdi <- data.frame(agey=c(1,5), vid = vidi , dummy=1, yearf = "2012")
  foii <- avgFOI(fitp_sea ,newdata=newdi,a1=1,a2=5,nreps=10000)
  res <- data.frame(vid = vidi, foii)
  res
}
#------------------------------------
# store average community-level FOI estimates and their uncertainty for
# use in the comparison with other community-level S. mansoni metrics
# and down-stream data visualizations
#------------------------------------
write_rds(foi_community_ests,path = here("output","mbita-village-foi.rds"))

```


# Repeat estimates at baseline in 2012

Since the study took place in the context of annual mass drug administration (MDA), which could influence SEA seroprevalence, examine age-specific patterns in 2012, pre-MDA, to ensure that treatment does not radically change age-dependent patterns. The 2012 estimates are consistent with estimates across all years. The force of infection increased more steeply in 2012 and decreased thereafter, but there was a lot of uncertainty owing to smaller sample size in 2012 (n=1120) compared with all three years combined (n=3663).

## Seroprevalence in 2012
```{r agecurves seroprev in year 1}

# Year 1, 2012
fitp_sea1 <- mgcv::gam(sea_pos~s(agey,bs="cr",k=9) + s(vid,bs="re",by=dummy),
                       family=binomial(link = "cloglog"), 
                       data=d3 %>% filter(year==2012))
newd <- d3 %>% filter(year==2012) %>%  mutate(dummy=0)
set.seed(127123)
fitp_sea1ci <- gamCI(m=fitp_sea1,newdata=newd,nreps=10000)

# convert linear predictor to prevalance
fitp_sea1ci <- fitp_sea1ci %>%
  mutate(fit = cloglogfn(fit),
         uprP = cloglogfn(uprP),
         lwrP = cloglogfn(lwrP),
         uprS = cloglogfn(uprS),
         lwrS = cloglogfn(lwrS),
         yearf = factor(year)
         )

```

Make a figure
```{r seroprev by age plot in year 1}

pageprev_y1 <- ggplot(data=fitp_sea1ci,aes(x=agey,y=fit)) +
  geom_ribbon(aes(ymin=lwrS,ymax=uprS),alpha=0.3, color = NA) +
  geom_line(lwd=0.5,alpha=1) +
  scale_y_continuous(breaks=seq(0,0.8,by=0.1),labels=seq(0,80,by=10))+
  labs(x="age, years",y="SEA seroprevalence (%)") +
  coord_cartesian(xlim=c(0,5),ylim=c(0,0.8))+
  theme_minimal() +
  theme(legend.position="right")

pageprev_y1

```

## Age-specific FOI in 2012

```{r estimate foi from seroprevalence in year 1}

#----------------------------------------
# Model predictions of FOI, with age grid newd
#----------------------------------------
set.seed(123)
newd <- data.frame(agey=seq(0.2,5,by=0.01),vid="1",dummy=0)
foi_ests1 <- foiCI(m=fitp_sea1,newdata=newd,fdvar="agey")
```

```{r foi by age in year 1 figure}
foiplot1 <- ggplot(data=foi_ests1,aes(x=agey,y=foi,ymin=foi_lwrBS,ymax=foi_uprBS)) +
  geom_ribbon(color=NA,alpha=0.3,fill="gray40") +
  geom_line(color="gray40") +
  scale_y_continuous(breaks=seq(0,0.6,by=0.1))+
  labs(x="age, years",y=expression(paste("age-specific seroconversion rate per year, ",lambda,"(a)")))+
  coord_cartesian(ylim=c(0,0.6))+
  theme_minimal()
foiplot1
```


# Figures 4C, 4D Analyses stratified by distance

In the descriptive analyses, most villages further than 1.5 km of Lake Victoria had distinctly lower village-specific estimates of force of infection.  Stratify the age-seroprevalence curves and age-specific force of infection estimates by distance from the lake.

## Fit a stratified seroprevalence model

```{r analysis by 1500m}
#-----------------------------
# create an indicator for 
# children living in villages
# more than 1500 meters from
# lake victoria.  This distance
# was chosen by inspection of
# village-specific FOI estimates
#-----------------------------
d4 <- d3 %>%
  mutate(gt15 = ifelse(dist_victoria>1500,1,0),
         lt15 = ifelse(dist_victoria<=1500,1,0),
         yearf = factor(year)
         )

#----------------------------------------
# fit a model allowing age-specific
# seroprevalence to vary by group
#----------------------------------------
fitp_dist <- mgcv::gam(sea_pos~s(agey,bs="cr",k=9,by=gt15) + 
                         s(agey,bs="cr",k=9,by=lt15) + 
                         s(vid,bs="re",by=dummy) +
                         yearf, 
                       family=binomial(link = "cloglog"), 
                       data=d4)
newd0 <- d4 %>%  mutate(dummy=0, yearf = "2012",gt15=0,lt15=1)
newd1 <- d4 %>%  mutate(dummy=0, yearf = "2012",gt15=1,lt15=0)
fitp_dist0_ci <- gamCI(m=fitp_dist,newdata=newd0,nreps=10000)
fitp_dist1_ci <- gamCI(m=fitp_dist,newdata=newd1,nreps=10000)

# convert linear predictor to prevalance
fitp_dist_ci <- bind_rows(fitp_dist0_ci,fitp_dist1_ci) %>%
  mutate(fit = cloglogfn(fit),
         uprP = cloglogfn(uprP),
         lwrP = cloglogfn(lwrP),
         uprS = cloglogfn(uprS),
         lwrS = cloglogfn(lwrS),
         ) %>%
  mutate(dist=factor(gt15,levels=c(0,1),labels=c("<1.5 km from lake",">1.5 km from lake")))

# Compare AIC and BIC
# with a model that does not allow 
# for separate baseline hazards by distance
# (estimated above, in an earlier code chunk)
AIC(fit_age_yr, fitp_dist)
BIC(fit_age_yr, fitp_dist)
```

## Figure of seroprevalence by age, stratified by distance from the lake

```{r figure of SEA seroprevalence by age stratified by distance}

#----------------------------------------
# seroprevalence curves
#----------------------------------------
distcols <- c(cbPalette[c(2)],vircols[3])
pageprev_sea01 <- ggplot(data=fitp_dist_ci,aes(x=agey,y=fit,group=dist,color=dist,fill=dist)) +
  geom_ribbon(aes(ymin=lwrS,ymax=uprS),alpha=0.2,color=NA) +
  geom_line(lwd=0.5,alpha=1) +
  scale_color_manual(values=distcols,guide=guide_legend(title=""))+
  scale_fill_manual(values=distcols,guide=FALSE)+
  scale_y_continuous(breaks=seq(0,1,by=0.2),labels=seq(0,100,by=20))+
  labs(x=NULL,y="seroprevalence (%)",tag = "C") +
  coord_cartesian(ylim=c(0,1),xlim=c(0,5))+
  theme_minimal() +
  theme(legend.position=c(0.3,0.9))

pageprev_sea01

```

## Estimate FOI, stratified by distance from the lake

```{r foi by distance}
#----------------------------------------
# Conditional estimates of FOI
#----------------------------------------
set.seed(123)
newd0 <- data.frame(agey=seq(0.2,5,by=0.01),gt15=0,lt15=1,yearf="2012",vid="1",dummy=0)
newd1 <- data.frame(agey=seq(0.2,5,by=0.01),gt15=1,lt15=0,yearf="2012",vid="1",dummy=0)
foi_ests0 <- foiCI(m=fitp_dist,newdata=newd0,fdvar="agey")
foi_ests1 <- foiCI(m=fitp_dist,newdata=newd1,fdvar="agey")
foi_dist <- bind_rows(foi_ests0,foi_ests1) %>%
  mutate(dist=factor(gt15,levels=c(0,1),labels=c("<1.5 km from lake",">1.5 km from lake")))
```

## Figure of FOI by age, stratified by distance from the lake
```{r figure of foi by age stratified by distance from lake}
#----------------------------------------
# FOI curves
#----------------------------------------
foiplot2 <- ggplot(data=foi_dist,aes(x=agey,y=foi,ymin=foi_lwrS,ymax=foi_uprS,group=dist,color=dist,fill=dist)) +
  # approximate simultaneous 95% CI
  geom_ribbon(color=NA,alpha=0.3) +
  # spline fits
  geom_line() +
  scale_color_manual(values=distcols,guide=guide_legend(title=""))+
  scale_fill_manual(values=distcols,guide=FALSE)+
  scale_y_continuous(breaks=seq(0,1,by=0.2))+
  labs(x="age, years",y=expression(paste("age-specific force of infection, ",lambda,"(a)")), tag = "D") +
  coord_cartesian(ylim=c(0,1))+
  theme_minimal() +
    theme(legend.position=c(0.3,0.9))
foiplot2

```

Create a composite figure for 4c and 4d
```{r comp figure for SEA, fig.width=6, fig.height = 8}

comp_sea_dist <- grid.arrange(pageprev_sea01,foiplot2,nrow = 2, ncol = 1)
ggsave(filename=here("output","mbita-SEA-by-age-dist.png"),plot=comp_sea_dist,device="png",width=3*1.18,height=6)

```

# Figure S5

Sensitivity analysis of distance ranges

Stratify the 30 villages into qunitiles of distance and repeat the age-dependent analyses

## Separate communities into 5 groups by quintiles of distance
```{r distance strata}
#----------------------------------------
# Identify distance qunitiles
#----------------------------------------
dvil <- d4 %>%
  group_by(vid) %>%
  slice(1) %>%
  dplyr::select(vid,dist_victoria)

dist_qs <- quantile(dvil$dist_victoria,probs=seq(0,1,by=0.2))

dist_cat <- dvil %>%
  mutate(distq = cut(dist_victoria,breaks=c(0,dist_qs[2:5],10000),labels=FALSE)) %>%
  dplyr::select(vid,distq) %>%
  mutate(distq=factor(distq,levels=1:5,labels=paste0("Q",1:5)))
  
```

## Fit a stratified seroprevalence model by quntiles

```{r analysis by distq}
#-----------------------------
# create indicators for 
# children living in qunitiles
# of distance from lake victoria.
#-----------------------------
d5 <- d4 %>%
  left_join(dist_cat,by="vid") %>%
  mutate(dq1 = ifelse(distq=="Q1",1,0),
         dq2 = ifelse(distq=="Q2",1,0),
         dq3 = ifelse(distq=="Q3",1,0),
         dq4 = ifelse(distq=="Q4",1,0),
         dq5 = ifelse(distq=="Q5",1,0),
         )

#----------------------------------------
# fit a model allowing age-specific
# seroprevalence to vary by group
#----------------------------------------
fitp_distq <- mgcv::gam(sea_pos~s(agey,bs="cr",k=5,by=dq1) +
                          s(agey,bs="cr",k=5,by=dq2) +
                          s(agey,bs="cr",k=5,by=dq3) +
                          s(agey,bs="cr",k=5,by=dq4) +
                          s(agey,bs="cr",k=5,by=dq5) +
                          s(vid,bs="re",by=dummy),
                       family=binomial(link = "cloglog"),
                       data=d5)

#----------------------------------------
# prediction datasets with distance set to each quintile
#----------------------------------------
newd1 <- d5 %>%  mutate(dummy=0,dq1=1,dq2=0,dq3=0,dq4=0,dq5=0)
newd2 <- d5 %>%  mutate(dummy=0,dq1=0,dq2=1,dq3=0,dq4=0,dq5=0)
newd3 <- d5 %>%  mutate(dummy=0,dq1=0,dq2=0,dq3=1,dq4=0,dq5=0)
newd4 <- d5 %>%  mutate(dummy=0,dq1=0,dq2=0,dq3=0,dq4=1,dq5=0)
newd5 <- d5 %>%  mutate(dummy=0,dq1=0,dq2=0,dq3=0,dq4=0,dq5=1)

#----------------------------------------
# estimate fitted values and simultaneous 95% CIs for each
# distance qunitile. Note, all curves are age-standardized across
# the entire study population
#----------------------------------------
fitp_distq1_ci <- gamCI(m=fitp_distq,newdata=newd1,nreps=10000)
fitp_distq2_ci <- gamCI(m=fitp_distq,newdata=newd2,nreps=10000)
fitp_distq3_ci <- gamCI(m=fitp_distq,newdata=newd3,nreps=10000)
fitp_distq4_ci <- gamCI(m=fitp_distq,newdata=newd4,nreps=10000)
fitp_distq5_ci <- gamCI(m=fitp_distq,newdata=newd5,nreps=10000)

#----------------------------------------
# convert linear predictor to prevalance
#----------------------------------------
fitp_distq_ci <- bind_rows(fitp_distq1_ci,fitp_distq2_ci,fitp_distq3_ci,fitp_distq4_ci,fitp_distq5_ci) %>%
  mutate(fit = cloglogfn(fit),
         uprP = cloglogfn(uprP),
         lwrP = cloglogfn(lwrP),
         uprS = cloglogfn(uprS),
         lwrS = cloglogfn(lwrS),
         )

#----------------------------------------
# format distance qunitile variable
# for plotting
#----------------------------------------
dist_qs_labs <- c(
  paste0("Q1: (",sprintf("%1.0f",dist_qs[1])," - ",sprintf("%1.0f",dist_qs[2]),"]"),
  paste0("Q2: (",sprintf("%1.0f",dist_qs[2])," - ",sprintf("%1.0f",dist_qs[3]),"]"),
  paste0("Q3: (",sprintf("%1.0f",dist_qs[3])," - ",sprintf("%1.0f",dist_qs[4]),"]"),
  paste0("Q4: (",sprintf("%1.0f",dist_qs[4])," - ",sprintf("%1.0f",dist_qs[5]),"]"),
  paste0("Q5: (",sprintf("%1.0f",dist_qs[4])," - ",sprintf("%1.0f",max(dvil$dist_victoria)),"]")
)

fitp_distq_ci <- fitp_distq_ci %>%
    mutate(distq = NA,
         distq = ifelse(dq1 == 1,dist_qs_labs[1],distq),
         distq = ifelse(dq2 == 1,dist_qs_labs[2],distq),
         distq = ifelse(dq3 == 1,dist_qs_labs[3],distq),
         distq = ifelse(dq4 == 1,dist_qs_labs[4],distq),
         distq = ifelse(dq5 == 1,dist_qs_labs[5],distq)
  )

```

## Figure of seroprevalence by age, stratified by distance quintiles

```{r figure of SEA seroprevalence by age stratified by distance qunitiles}

#----------------------------------------
# seroprevalence curves
#----------------------------------------
distqcols <- cbPalette[c(3,2,4,7,6)]
pageprev_sea_distq <- ggplot(data=fitp_distq_ci,aes(x=agey,y=fit,group=distq,color=distq,fill=distq)) +
  # geom_ribbon(aes(ymin=lwrS,ymax=uprS),alpha=0.2,color=NA) +
  geom_line(lwd=0.5,alpha=1) +
  scale_color_manual(values=distqcols,guide=guide_legend(title="distance quintile (m)"))+
  scale_fill_manual(values=distqcols,guide=FALSE)+
  scale_y_continuous(breaks=seq(0,1,by=0.2),labels=seq(0,100,by=20))+
  labs(x="age, years",y="seroprevalence (%)") +
  coord_cartesian(ylim=c(0,1),xlim=c(0,5))+
  theme_minimal() +
  theme(legend.position=c(0.3,0.8),
        legend.text = element_text(size=8),
        legend.key.height= unit(0.3,units="cm"))

pageprev_sea_distq

# save png file
ggsave(filename=here("output","mbita-sea-age-seroprev-distq.png"),plot=pageprev_sea_distq,device="png",width=3*1.18,height=3)

```

# Session Info
```{r session info}
sessionInfo()
```


