---
title: "Fine-scale heterogeneity in Schistosoma mansoni force of infection measured through antibody response"
subtitle: "Figure S1, S. mansoni SEA and Sm25 antibody distributions"
author: "Ben Arnold ben.arnold@ucsf.edu"
date: "run `r Sys.time()`"
output: 
  html_document:
    highlight: haddock
    theme: default
    code_folding: hide
    df_print: paged
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


# Preamble
```{r preamble}
library(here)
here()
#--------------------------------
# source the configuration file
#--------------------------------
source(here("R/mbita-schisto-Config.R"))
```


# Load and process data
```{r load data,message=FALSE,warning=FALSE}


#---------------------------
# mbita PSAC data
#---------------------------
d <- readRDS(here("data","mbita_schisto.rds") )


#---------------------------
# log-transform the MFI
# values
# set values at or below 0
# to missing before the 
# transform
#---------------------------
d2 <- d %>%
  mutate(logsea = ifelse(sea <=0, NA, log10(sea)),
         logsm25 = ifelse(sm25 <= 1, NA, log10(sm25)))

#---------------------------
# pivot the data longer to
# make it easier to plot
#---------------------------

d3 <- d2 %>%
  dplyr::select(year,vid,pid,agey,logsea,logsm25) %>%
  pivot_longer(cols = c(logsea,logsm25), names_to = "antigen", names_prefix = "log", values_to = "logmfi") %>%
  mutate(antigenf = case_when(
    antigen == "sea" ~ "SEA",
    antigen == "sm25" ~ "Sm25"
  ), 
  antigenf = factor(antigenf,levels = c("SEA","Sm25"))
  )
#---------------------------
# store SEA and Sm25 ROC cutoffs
# these cutoffs were provided
# by Kim Won in the file
# Mbita cutoff table for Ben.xlsx
#---------------------------
dcuts <- data.frame(antigenf = c("SEA","Sm25"), cutroc = c(log10(965), log10(38) ))


```

# Figure S1

## MFI by age

```{r mfi by age, warning= FALSE}

pcols <- c(vircols[3],cbPalette[2])
log10labs <- c( 
  expression(10^0),
  expression(10^1),
  expression(10^2),
  expression(10^3),
  expression(10^4)
)

pmfiage <- ggplot(data = d3, aes(x = agey, y = logmfi, color = antigenf)) +
  facet_grid(antigenf~.) +
  geom_point(size = 0.5, alpha = 0.3) +
  geom_hline(data = dcuts, aes(yintercept = cutroc),lwd = 0.25,col = "gray20") +
  # geom_smooth(method = "loess", se = FALSE, lwd = 0.5, color = "gray20") +
  scale_color_manual(values = pcols) +
  scale_y_continuous(breaks = 0:4, labels = log10labs) +
  labs(x = "age, years", y = "Luminex response (MFI-bg)", tag = "A") +
  coord_cartesian(ylim = c(0,4.5)) +
  theme(
    legend.position = "none",
    strip.text.y = element_blank()
  )


```

## Antibody level distributions

```{r mfi distributions, warning= FALSE}
pcols <- c(vircols[3],cbPalette[2])
log10labs <- c( 
  expression(10^0),
  expression(10^1),
  expression(10^2),
  expression(10^3),
  expression(10^4)
)

nobs <- length(d3$logmfi[d3$antigen=="sea"])
hbreaks <- seq(0,4.6,by=0.05)
pmfidist <- ggplot(data = d3, aes(x = logmfi, color = antigenf, fill = antigenf)) +
  facet_grid(antigenf~.) +
  # geom_line(stat = "density") +
  geom_histogram(aes(x = logmfi), breaks = hbreaks, color = NA, alpha = 0.8)+
  geom_vline(data = dcuts, aes(xintercept = cutroc),lwd = 0.25,col = "gray20") +
  scale_color_manual(values = pcols) +
  scale_fill_manual(values = pcols) +
  scale_x_continuous(breaks = 0:4, labels = log10labs) +
  scale_y_continuous(expand = c(0,0), breaks = seq(0,700,by=100))+
  labs(x = NULL, y = "N observations", tag = "B") +
  coord_flip(ylim = c(0,700), xlim = c(0,4.5))+
  theme(
    legend.position = "none", 
    strip.text.y = element_text(angle = 0)
  )


```

## Combined figure

```{r combined figure, warning= FALSE}
pcomp <- grid.arrange(pmfiage,pmfidist,nrow = 1, ncol =2)

ggsave(here("output","mbita-schisto-ab-distributions.png"),pcomp,device = "png")
```

## Extra: plot age-dependent mean and seroprevalence

Sm25 is not included in the main analyses, but examine age-dependent mean and seroprevalence for completeness. Simply use `ggplot`'s internal smoother (no 95% CIs because it does not account for clustering on village).
```{r plot age dependent means}
plot_age_means <- ggplot(data=d3, aes(x = agey, y = logmfi, color = antigenf)) + 
  geom_smooth(se = FALSE) +
  scale_color_manual(values = pcols, guide=guide_legend(title = "Antigen")) +
  scale_y_continuous(breaks = 0:4, labels = log10labs) +
  labs(x = "age, years", y = "Luminex response (MFI-bg)", tag = "A") +
  coord_cartesian(ylim = c(0,4.5)) 

plot_age_means

```


```{r plot age dependent seroprevalence}
d4 <- d3 %>%
  mutate(serocut = ifelse(antigenf == "SEA",log10(965),log10(38)),
         seropos = ifelse(logmfi>serocut,1,0)
         )

plot_age_serop <- ggplot(data=d4, aes(x = agey, y = seropos, color = antigenf)) + 
  geom_smooth(se = FALSE) +
  scale_color_manual(values = pcols, guide=guide_legend(title = "Antigen")) +
  scale_y_continuous(breaks = seq(0,1,by=0.2), labels = sprintf("%1.0f",seq(0,1,by=0.2)*100)) +
  labs(x = "age, years", y = "Seroprevalence (%)", tag = "B") +
  coord_cartesian(ylim = c(0,1)) 

plot_age_serop
```



# Session Info
```{r session info}
sessionInfo()
```
