---
title: "Mbita, Kenya schistosomiasis study. Analysis of distance from Lake Victoria"
output:
  html_document:
    highlight: haddock
    theme: default
    code_folding: hide
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


# Preamble
```{r preamble}
library(here)
here()
#--------------------------------
# source the configuration file
#--------------------------------
source(here("R/mbita-schisto-Config.R"))

#--------------------------------
# source the shared functions file
#--------------------------------
source(here("R/mbita-schisto-Functions.R"))
```



# Load Mbita Kenya antibody measurements and other data

These data include measurements from pre-school aged children in 30 villages near Homa Bay and Mbita in Western Kenya. This article summarizes the study design and field methods:

Won KY, Kanyi HM, Mwende FM, Wiegand RE, Brook Goodhew E, Priest JW, et al. Multiplex Serologic Assessment of Schistosomiasis in Western Kenya: Antibody Responses in Preschool Age Children as a Measure of Reduced Transmission. _Am J Trop Med Hyg._ 2017; 16–0665. https://www.ncbi.nlm.nih.gov/pubmed/28719280

```{r load data, warning=FALSE}
#-----------------------------------
# load the child antibody and 
# kato-katz measurements
#-----------------------------------
d <- readRDS(here("data","mbita_schisto.rds")) %>%
  mutate(vid=factor(vid))

#-----------------------------------
# load the village-level spatial
# covariate data, created with
# mbita-schisto-map.Rmd
#
# note: for public-facing workflow
# this file does not include village 
# lon/lat to protect participant
# confidentiality
#-----------------------------------
d_spatial <- readRDS(here("data","mbita_spatial.rds")) %>%
  mutate(vid=factor(vid))

d2 <- d %>%
  left_join(d_spatial,by="vid")

# create age strata
# create log values for SEA MFI and KK epg
# convert the dist_victoria variable from class units to numeric
# add a dummy variable for modeling
d2 <- d2 %>%
  mutate(agecat = cut(agey,breaks=c(0,1,2,3,4,6),
                      labels=c("<1 year","1 year","2 years","3 years","4 years")),
         logsea = log10(sea),
         logepg = log10(sm_epg),
         dist_victoria = as.numeric(dist_victoria),
         dummy=1
         )

#-----------------------------------
# load village-level FOI estimates
# estimated in the notebook
# mbita-schisto-SEA-vs_KK.Rmd
#-----------------------------------
d_foi <- readRDS(here("output","mbita-village-foi.rds"))

#-----------------------------------
# create a village-level summary
# dataset of spatial covariates,
# prevalence, and FOI for making figures
#-----------------------------------

dvil <- d2 %>%
  group_by(vid) %>%
  summarize(sea_n = sum(sea_pos,na.rm=T),
            sea_N = sum(ifelse(!is.na(sea_pos),1,0)),
            kk_n = sum(kk_pos,na.rm=T),
            kk_N = sum(ifelse(!is.na(kk_pos),1,0)),
            arm = max(arm)
            ) %>%
  mutate(sea_prev = sea_n/sea_N,
         kk_prev = kk_n/kk_N)
  
# join FOI estimates
dvil2 <- left_join(dvil,d_foi,by="vid")

# join spatial covariates
dvil3 <- left_join(dvil2,d_spatial,by="vid") %>%
  mutate(dist_victoria = as.numeric(dist_victoria))

```


# Village-level seroprevalence and FOI versus distance from the lake

## Fit models of prevalence by distance

Estimate seroprevalence as a function of distance from Lake Victoria using a semi-parametric spline

```{r seroprevalence vs dist}
#-----------------------------
# spline model of SEA seroprevalence
# by distance from the lake
# 
# include village-level random
# effects to account for within-
# village correlation
#-----------------------------

fit_sea_dist <- mgcv::gam(sea_pos~s(dist_victoria,bs="cr",k=4) + s(vid,bs="re",by=dummy),
                          family="binomial",
                          data=d2)
newd <- d2 %>% filter(dist_victoria < 4000) %>% mutate(dummy=0)
fit_sea_dist_ci <- gamCI(m=fit_sea_dist,newdata=newd,nreps=10000)

# convert linear predictor to prevalance 
# (note: expitfn() is in shared functions, source above)
fit_sea_dist_ci <- fit_sea_dist_ci %>%
  mutate(fit = expitfn(fit),
         uprP = expitfn(uprP),
         lwrP = expitfn(lwrP),
         uprS = expitfn(uprS),
         lwrS = expitfn(lwrS),
         )

```

Estimate Kato-Katz prevalence as a function of distance from Lake Victoria using a semi-parametric spline

```{r kk prevalence vs dist}
#-----------------------------
# spline model of SEA seroprevalence
# by distance from the lake
#-----------------------------

fit_kk_dist <- mgcv::gam(kk_pos~s(dist_victoria,bs="cr",k=4) + s(vid,bs="re",by=dummy), 
                         family="binomial",
                         data=d2)
newd <- d2 %>% filter(dist_victoria < 4000) %>% mutate(dummy=0)
fit_kk_dist_ci <- gamCI(m=fit_kk_dist,newdata=newd,nreps=10000)

# convert linear predictor to prevalance 
# (note: expitfn() is in shared functions, source above)
fit_kk_dist_ci <- fit_kk_dist_ci %>%
  mutate(fit = expitfn(fit),
         uprP = expitfn(uprP),
         lwrP = expitfn(lwrP),
         uprS = expitfn(uprS),
         lwrS = expitfn(lwrS),
         )

```

## KK prevalence vs. distance

```{r KK prev vs distance fig}
#-----------------------------
# KK prevalence by distance
#-----------------------------
pkkdist <- ggplot(data=fit_kk_dist_ci,aes(x=dist_victoria/1000)) +
  geom_line(aes(y=fit), color="gray40",lwd=0.3) +
  # geom_ribbon(aes(ymin=lwrP,ymax=uprP),alpha=0.1,color=NA,fill="black") +
  # geom_ribbon(aes(ymin=lwrS,ymax=uprS),alpha=0.1,color=NA,fill="black") +
  geom_point(data=dvil3,aes(x=dist_victoria/1000,y=kk_prev),alpha=1,color=cbPalette[2]) +
  scale_y_continuous(breaks=seq(0,1,by=0.2),labels=sprintf("%1.0f",seq(0,1,by=0.2)*100))+
  scale_x_continuous(breaks=0:5)+
  # scale_color_manual(values=pcols)+
  coord_cartesian(ylim=c(0,0.9),xlim=c(0,3.5)) +
  labs(x="distance from lake Victoria (km)",y="community prevalence (%)") +
  theme_minimal() +
  theme(legend.position="none")
pkkdist

```

## SEA seroprevalence vs. distance
```{r SEA seroprev vs distance fig}
#-----------------------------
# SEA seroprevalence by distance
#-----------------------------
pspdist <- ggplot(data=fit_sea_dist_ci,aes(x=dist_victoria/1000)) +
  geom_line(aes(y=fit), color="gray40",lwd=0.3) +
  # geom_ribbon(aes(ymin=lwrP,ymax=uprP),alpha=0.1,color=NA,fill="black") +
  # geom_ribbon(aes(ymin=lwrS,ymax=uprS),alpha=0.1,color=NA,fill="black") +
  geom_point(data=dvil3,aes(x=dist_victoria/1000,y=sea_prev),alpha=1,color=cbPalette[3]) +
  scale_y_continuous(breaks=seq(0,1,by=0.2),labels=sprintf("%1.0f",seq(0,1,by=0.2)*100))+
  scale_x_continuous(breaks=0:5)+
  # scale_color_manual(values=pcols)+
  coord_cartesian(ylim=c(0,0.9),xlim=c(0,3.5)) +
  labs(x="distance from lake Victoria (km)",y="community seroprevalence (%)") +
  theme_minimal() +
  theme(legend.position="none")
pspdist

# save png file
ggsave(filename=here("output","mbita-SEA-seroprev-v-dist.png"),plot=pspdist,device="png",width=3*1.18,height=3)

```

## SEA FOI vs. distance
```{r SEA FOI vs distance fig}
#-----------------------------
# FOI measured by SEA seroconversion over by distance
#-----------------------------
pfoidist <- ggplot(data=dvil3,aes(x=dist_victoria/1000,y=lambda)) +
  geom_point(alpha=1,color=cbPalette[3]) +
  # geom_vline(xintercept = 1.5, lty = "dashed") +
  scale_y_continuous(breaks=seq(0,0.6,by=0.1))+
  scale_x_continuous(breaks=0:5)+
  # scale_color_manual(values=pcols)+
  coord_cartesian(ylim=c(0,0.65),xlim=c(0,3.5)) +
  labs(x="distance from lake Victoria (km)",y=expression(paste("seroconversion rate per year (",lambda,")"))) +
  theme_minimal() +
  theme(legend.position="none")
pfoidist

# save png file
ggsave(filename=here("output","mbita-SEA-foi-v-dist.png"),plot=pfoidist,device="png",width=3*1.18,height=3)
```



# Repeat figures, colored by intervention arm

Repeat the figures above, coloring the points by intervention arm to ensure the patterns are not driven by community-level versus school-based praziquantle distribution

```{r KK prev vs distance colored by arm fig}
#-----------------------------
# KK prevalence by distance
# points colored by intervention arm
#-----------------------------
pkkdist2 <- ggplot(data=fit_kk_dist_ci,aes(x=dist_victoria/1000,color=arm)) +
  geom_point(data=dvil3,aes(x=dist_victoria/1000,y=kk_prev),alpha=0.9) +
  geom_line(aes(y=fit), color="gray40",lwd=0.3) +
  # geom_ribbon(aes(ymin=lwrP,ymax=uprP),alpha=0.1,color=NA,fill="black") +
  # geom_ribbon(aes(ymin=lwrS,ymax=uprS),alpha=0.1,color=NA,fill="black") +
  scale_y_continuous(breaks=seq(0,1,by=0.2),labels=sprintf("%1.0f",seq(0,1,by=0.2)*100))+
  scale_x_continuous(breaks=0:5)+
  scale_color_manual(values=cbPalette[c(4,8)])+
  coord_cartesian(ylim=c(0,0.9),xlim=c(0,3.5)) +
  labs(x="distance from lake Victoria (km)",y="community prevalence (%)") +
  theme_minimal() +
  theme(legend.position="right")
pkkdist2
```

```{r SEA seroprev vs distance colored by arm fig}
#-----------------------------
# SEA seroprevalence by distance
# points colored by intervention arm
#-----------------------------
pspdist2 <- ggplot(data=fit_sea_dist_ci,aes(x=dist_victoria/1000,color=arm)) +
  geom_point(data=dvil3,aes(x=dist_victoria/1000,y=sea_prev),alpha=0.9) +
  geom_line(aes(y=fit), color="gray40",lwd=0.3) +
  # geom_ribbon(aes(ymin=lwrP,ymax=uprP),alpha=0.1,color=NA,fill="black") +
  # geom_ribbon(aes(ymin=lwrS,ymax=uprS),alpha=0.1,color=NA,fill="black") +
  scale_y_continuous(breaks=seq(0,1,by=0.2),labels=sprintf("%1.0f",seq(0,1,by=0.2)*100))+
  scale_x_continuous(breaks=0:5)+
  scale_color_manual(values=cbPalette[c(4,8)])+
  coord_cartesian(ylim=c(0,0.9),xlim=c(0,3.5)) +
  labs(x="distance from lake Victoria (km)",y="community seroprevalence (%)") +
  theme_minimal() +
  theme(legend.position="right")
pspdist2
```


```{r SEA FOI vs distance colored by arm fig}
#-----------------------------
# FOI measured by SEA seroconversion over by distance
# points colored by intervention arm
#-----------------------------
pfoidist2 <- ggplot(data=dvil3,aes(x=dist_victoria/1000,y=lambda,color=arm)) +
  geom_point(alpha=0.9) +
  scale_y_continuous(breaks=seq(0,0.6,by=0.1))+
  scale_x_continuous(breaks=0:5)+
  scale_color_manual(values=cbPalette[c(4,8)])+
  coord_cartesian(ylim=c(0,0.65),xlim=c(0,3.5)) +
  labs(x="distance from lake Victoria (km)",y=expression(paste("seroconversion rate per year (",lambda,")"))) +
  theme_minimal() +
  theme(legend.position="right")
pfoidist2
```


# Session Info
```{r session info}
sessionInfo()
```


