---
title: "Mbita, Kenya schistosomiasis study. Preprocess the data"
output:
  html_document:
    highlight: haddock
    theme: default
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


# Preamble
```{r preamble}
library(here)
here()
#--------------------------------
# source the configuration file
#--------------------------------
source(here("R/mbita-schisto-Config.R"))
```



# Load Mbita Kenya antibody measurements

These data include measurements from pre-school aged children in 30 villages near Homa Bay and Mbita in Western Kenya. This article summarizes the study design and field methods:

Won KY, Kanyi HM, Mwende FM, Wiegand RE, Brook Goodhew E, Priest JW, et al. Multiplex Serologic Assessment of Schistosomiasis in Western Kenya: Antibody Responses in Preschool Age Children as a Measure of Reduced Transmission. _Am J Trop Med Hyg._ 2017; 16–0665. https://www.ncbi.nlm.nih.gov/pubmed/28719280

The script below loads the full dataset, limits it to variables relevant to the present analysis for public distribution, and stores village latitude and longitude in a separate file (not publicly shared) to protect participant confidentiality.

NOTE: This script is provided for completness but cannot be run publicly because the raw, underlying data are not available.

```{r load data}
d <- readRDS(here("data","mbita_psac.rds"))

d2 <- d %>%
  dplyr::select(year,vid,arm,pid,agey,sex,sea,sm25,sm_epg)

#---------------------------
# identify seropositive by
# SEA and Sm25 using ROC cutoff
# these cutoffs were provided
# by Kim Won in the file
# Mbita cutoff table for Ben.xlsx
#---------------------------
d2 <- d2 %>%
  mutate(
    sea_pos = ifelse(sea>965,1,0),
    sm25_pos = ifelse(sm25>38,1,0),
    kk_pos = ifelse(sm_epg>0,1,0)
  )


d_lonlat <- d %>%
  dplyr::select(vid,lon,lat) %>%
  group_by(vid) %>%
  slice(1)

saveRDS(d2,file=here("data","mbita_schisto.rds"))
saveRDS(d_lonlat,file=here("data","mbita_lonlat.rds"))

```


# Session Info
```{r session info}
sessionInfo()
```
